\beginsong{Redemption Song}[by={Bob Marley}]

%\gtab{G7}{320001}

%\chordson

%\gtab{Bm9}{7:131113}
%\gtab{A/B}{9:14312X}
%\gtab{Em}{7:XX3321}
%\gtab{F#7}{242322}



\beginverse
\nolyrics Intro: \[G]
\endverse

\beginverse

Old p\[G]irates, yes, they r\[Em]ob I
Sold I t\[C]o the merchant sh\[Am]ips
M\[G]inutes after they t\[Em]ook I
Fr\[C]om the bottomless p\[D]it
But my h\[G]and was made str\[Em]ong
By the h\[C]and of the alm\[Am]ighty
We f\[G]orward in this gener\[Em]ation
\[C]Triumphantly\[D]

\endverse

\beginchorus
Won't you help to s\[G]ing? \[C] These s\[D]ongs of fr\[G]eedom?
'Cause \[C]all I \[D]ever have. \[Em] \[C] Red\[D]emption s\[G]ongs, \[C] Red\[D]emption s\[G]ongs \[C D]
\endchorus

\beginverse
Emancipate yourselves from mental slavery
None but ourselves can free our minds
Have no fear for atomic energy
'Cause none of them can stop the time
How long shall they kill our prophets
While we stand aside and look? Ooh
Some say it's just a part of it
We've got to fullfil the book
\endverse

\beginchorus
Won't you help to s\[G]ing? \[C] These s\[D]ongs of fr\[G]eedom?
'Cause \[C]all I \[D]ever have. 
                  
\[Em] \[C] Red\[D]emption s\[G]ongs, \[C] Red\[D]emption s\[G]ongs, \[C] Red\[D]emption s\[G]ongs \[C D]
\endchorus

\beginverse
\nolyrics \[Em C D] 
           
          
\[Em C D]
\endverse

\beginverse
Emancipate yourselves from mental slavery
None but ourselves can free our mind
Woh, have no fear for atomic energy
'Cause none of them-a can-a stop-a the time
How long shall they kill our prophets
While we stand aside and look?
Yes, some say it's just a part of it
We've got to fullfill the book
\endverse

\beginchorus \chordsoff
Won't you help to sing
These songs of freedom?
'Cause all I ever had
Redemption songs
All I ever had
Redemption songs
These songs of freedom
Songs of freedom

\endchorus






\endsong
