\beginsong{Every You Every Me}[by={Placebo}]

%\gtab{G7}{320001}

%\chordson

%\gtab{Bm9}{7:131113}
%\gtab{A/B}{9:14312X}
%\gtab{Em}{7:XX3321}
%\gtab{F#7}{242322}



\beginverse

\nolyrics Intro: \[Dm Bb C] 4x
\endverse

\beginverse\memorize
\[Dm]Sucker l\[Bb]ove is h\[C]eaven s\[Dm]ent.
You pucker \[Bb]up, our p\[C]assion's sp\[Dm]ent.
My hearts a t\[Bb]art, your b\[C]ody's r\[Dm]ent.
My body's br\[Bb]oken, y\[C]ours is b\[Bb]ent.

C\[Bb]arve your name into my \[Dm]arm.
Instead of stressed, I lie here ch\[Bb]armed.
Cuz there's nothing else to d\[F]o,
Every m\[A]e and every y\[Dm]ou.

\endverse

\beginverse
S^ucker l^ove, a b^ox I ch^oose.
No other b^ox I ch^oose to ^use.
Another l^ove I w^ould ab^use,
No circumst^ances c^ould exc^use.

^In the shape of things to c^ome.
Too much poison come und^one.
Cuz there's nothing else to d^o,
Every m^e and every y\[Bb]ou. 
Every me and every y\[F]ou, 
Every M\[A]e...h\[Dm]e

\endverse

\beginverse
S^ucker l^ove is kn^own to sw^ing.
Prone to cl^ing and w^aste these th^ings.
Pucker ^up for h^eavens s^ake.
There's never b^een so m^uch at st^ake.

I s^erve my head up on a pl^ate.
It's only comfort, calling l^ate.
Cuz there's nothing else to d^o,
Every m^e and every y\[Bb]ou. Every me and every y\[F]ou, Every M\[A]e...h\[Bb]e

Every me and every y\[F]ou, Every M\[A]e...h\[Dm]e

\endverse

\beginverse

L^ike the n^aked l^eads the bl^ind.
I know I'm s^elfish, ^I'm unk^ind.
Sucker l^ove I ^always f^ind,
Someone to br^uise and l^eave beh^ind.

^All alone in space and t^ime.
There's nothing here but what here's m^ine.
Something borrowed, something bl^ue.
Every m^e and every y\[Bb]ou. Every me and every y\[F]ou, Every M\[A]e...h\[Bb]e

Every me and every y\[F]ou,  Every M\[A]e...h\[Bb]e [x3] 
Every me and every y\[F]ou,  Every M\[A]e...h\[Dm]e
\endverse



\endsong
